ResearchNotes

### 2014-07-25 ResearchNotes/ResearchNotes.Rmd
Just showed with the full models that there are 6% improvments vs statistically adjusted forecasts and 60% vs the raw forecast errors.  I get the feeling that that forecasts mean something different than I think.  That is just not right.

Quick summary is that google trends is helpful in all hours of the day. It also looks like the forecasts are usually off by a large amount.  I should look at those individually.

@@

>>>>

Quick summary is that Google trends is helpful in all hours of the day. It also looks like the forecasts are usually off by a large amount.  I should look at those individually.

@@

Given this I need to compare not just the difference between actual and forecast but the difference between with trends data and statistically adjusted forecast.  It is just not fair.

I will compare with the full model and via drop forward cross validation.

#Compare sigma on three models

For these comparisons I have to make sure I am using equal sized datasets.  So only those with trend data.

```{r}
WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]
```

Now create a function that compares the sigma of the two models.  I will call the one without Google trends data the statistically adjusted forecasts.

# Gives percent reduction in sigma
CompareSigma<-function(x){
SA<-summary(lm(HourModelForecastCheck(x), data=WTrendsLimited))$sigma  
Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma

(SA-Google)/(SA)
}

lapply(1:24, FUN = CompareSigma)
mean(unlist(lapply(1:24, FUN = CompareSigma)))

Nice percent savings vs the statistically adjusted model -- about 6% reduction average by hour.

Now make a comparison to raw

# Gives percent reduction in sigma
CompareRaw<-function(x){
SA<-sd(WTrendsLimited[,x]-WTrendsLimited[,30])  
Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma

(SA-Google)/(SA)
}

lapply(1:24, FUN = CompareRaw)
mean(unlist(lapply(1:24, FUN = CompareRaw)))

```
Man that is huge.  Damn huge.  I must be misunderstanding what they mean by forecast.

Time, to look at this from a drop forward point of view.

# Compare with drop forward crossvalidation

This will be a fairer comparison.  I will boot up each model with 15 observations that then look at how they predict the next day, updating the model each day.
